From Real-time Attention Assessment to ``With-me-ness'' in Human-Robot Interaction

### 2015-10-01 paper.tex
Commented out last fixme

Our approach relies on a simple, non-intrusive sensor (a RGB camera by the
robot) and an open-source, fast pose estimation algorithm\fixme{test on nao!
how fast is it actually?}: we hope that this may contribute to the widespread
adoption of such a technique on a range of robots, including the relatively
common {\sc nao} platform.

>>>>

Our approach relies on a simple, non-intrusive sensor (a RGB camera by the
robot) and an open-source, fast pose estimation algorithm
: we hope that this may contribute to the widespread
adoption of such a technique on a range of robots, including the relatively
common {\sc nao} platform.
%\fixme{test on nao! how fast is it actually? in 320x240, 240ms on nao, 20ms on core i7}
